Investigating Biases Associated with Dietary Starch Incorporation and Retention with an Oral Biofilm Model

### 2023-06-01 analysis/paper/matmet.Rmd
fix broken citekey

Pearson's *r* was conducted on sample weight and total starch count, as well as sample
weight and starch count per mg calculus. The total count for each sample within a
treatment was standardised by z-score to account for the differences in magnitude
between the potato and wheat counts.
This was applied to total biofilm weight and starch count per mg 
calculus (also z-score standardised) to account for differences in starch 
concentration in the calculus [as per 
@wesolowskiEvaluatingMicrofossilContent2010].

>>>>

Pearson's *r* was conducted on sample weight and total starch count, as well as sample
weight and starch count per mg calculus. The total count for each sample within a
treatment was standardised by z-score to account for the differences in magnitude
between the potato and wheat counts.
This was applied to total biofilm weight and starch count per mg 
calculus (also z-score standardised) to account for differences in starch 
concentration in the calculus [as per 
@wesolowskiEvaluatingMicrofossil2010].
